---
title: "A-quick-tour-of-GRMoE"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-quick-tour-of-GRMoE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 5.5,
	fig.width = 6,
	warning = FALSE,
	collapse = TRUE,
	dev.args = list(pointsize = 10),
	out.width = "90%",
	par = TRUE
)
knit_hooks$set(par = function(before, options, envir)
  { if (before && options$fig.show != "none") 
       par(family = "sans", mar = c(4.1,4.1,1.1,1.1), mgp = c(3,1,0), tcl = -0.5)
})
```

```{r, message = FALSE, echo = FALSE}
library(RMoE)
```

# Introduction

**GRMoE** (Gaussian Regularized Mixture-of-Experts) provides a penalized MLE 
for the regularized Normal Mixture of Experts. **GRMoE** consists of a mixture 
of *K* Normal expert regressors network) gated by a softmax gating network.

It was written in R Markdown, using the [knitr](https://cran.r-project.org/package=knitr) 
package for production.

See `help(package="RMoE")` for further details.

# Application to a simulated dataset

## Load data

```{r}
data("gaussian")
X <- as.matrix(gaussian[, -8])
y <- gaussian$V8
```

## Set up GRMoE model parameters

```{r}
K <- 2 # Number of experts
Lambda <- 5
Gamma <- 5
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type
```

## Estimation

```{r}
grmoe <- GaussRMoE(Xm = X, Ym = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)
```

## Parameters

You can access to the parameters via the following commands:

```{r}

# Regression coefficients for each expert
grmoe$betak

# Parameters of the gating network
grmoe$wk
```

## Plot

### Log-likelihood

```{r}
grmoe$plot(what = "loglik")
```

### Proportion of zero coefficients

```{r}
grmoe$plot(what = "zerocoefficients")
```

# Application to a real dataset

## Load data

```{r}
data("housing")
X <- as.matrix(housing[, -15])
y <- housing$V15
```

## Set up GRMoE model parameters

```{r}
K <- 2 # Number of experts
Lambda <- 42
Gamma <- 10
opt <- FALSE # opt = FALSE: proximal Newton; opt = TRUE: proximal Newton-type
```

## Estimation

```{r}
grmoe <- GaussRMoE(Xm = X, Ym = y, K = K, Lambda = Lambda, 
                   Gamma = Gamma, option = opt, verbose = TRUE)
```

## Parameters

You can access to the parameters via the following commands:

```{r}

# Regression coefficients for each expert
grmoe$betak

# Parameters of the gating network
grmoe$wk
```

## Plot

### Log-likelihood

```{r}
grmoe$plot(what = "loglik")
```

### Proportion of zero coefficients

```{r}
grmoe$plot(what = "zerocoefficients")
```
